---
title: "aer13_ReplicationAssignment"
author: "Abby_Robinson"
date: "11/10/2021"
output: html_document
---
```{r}
library(curl)
```

```{r}
f <- curl("https://raw.githubusercontent.com/butterfliesrcool/BI588_Replication_Assignment/main/Adelpha2016.csv")
count.data  <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
count.data
```
Summary Stats
```{r}
attacks <- subset(count.data, attacks >= "1", drop = FALSE)
attacks

aggregate(x= attacks$attacks, by= list(attacks$species), FUN=sum)

ag <- aggregate(x= attacks$attacks, by= list(attacks$day), FUN=sum)
ag
```
attacks by species by day 

```{r}
eva <- subset(count.data, species == "evarete", drop = FALSE)
aggregate(x= eva$attacks, by= list(eva$day), FUN=sum)
```

```{r}
iph <- subset(count.data, species == "iphiclus", drop = FALSE)
aggregate(x= iph$attacks, by= list(iph$day), FUN=sum)
```

```{r}
leu <- subset(count.data, species == "leucopthalma", drop = FALSE)
aggregate(x= leu$attacks, by= list(leu$day), FUN=sum)
```

```{r}
ser <- subset(count.data, species == "serpa", drop = FALSE)
aggregate(x= ser$attacks, by= list(ser$day), FUN=sum)
```
##figure 1a. of the paper is the proportion of facsimilies attacks, so the number of attacks/500 (the sample size)


Let's figure out all our attack totals! I think we maybe need to feed the survival scores into the survival package in order for this to work....

calculate survival scores per day and try to load them into the survival package? 

Things to do: 

1. general linear model with Poisson distribution
########Rubiaceae-feeding Adelpha iphiclus was attacked significantly less compared to the other three phenotypes, where ∗P < 0.03 for all comparisons 

3. Using a general linear model with Pois- son distribution, we found that A. iphiclus was attacked signifi- cantly less than the other three facsimile phenotypes (z-value = 2.399, d.f. = 399, P = 0.0164 vs J. evarete; z-value = 2.579, d.f. = 399, P = 0.0058 vs A. serpa; z-value = 2.306, d.f. = 399, P = 0.0211 vs A. leucopthalma). 

2. Survivorship curves show similar results where A. iphiclus has the highest overall survivorship compared to the other butterfly phenotypes (∗P < 0.02; Cox proportional-hazards regression model). Adelpha serpa, A. leucopthalma, and J. evarete survivorship did not differ significantly from one another (all P > 0.7, marked with NS)






