---
title: "binomial"
author: "Abby_Robinson"
date: "11/19/2021"
output: html_document
---
##chi squared approxiamation may be incorrect error: delete the zeros!!

```{r}
library(curl)
library(survival)
library(ggplot2)
library(survminer)
```

```{r}
f <- curl("https://raw.githubusercontent.com/butterfliesrcool/BI588_Replication_Assignment/main/Adelpha2016_binomial.csv")
data  <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
data
```

```{r}
eva <- subset(data, species == "evarete", drop = FALSE)
eva

chisq.test(table(eva$attacks, eva$day))
table(eva$attacks, eva$day)

survdiff(Surv(day, attacks) ~ day, data=eva)
pairwise_survdiff(Surv(day, attacks) ~ day, p.adjust.method = "BH",
     data = eva)
```


```{r}
attacks <- subset(data, attacks >= "1", drop = FALSE)
attacks
table(attacks$attacks, attacks$species)
```

```{r}
model <- survfit(Surv(day, day+1, attacks) ~ species, data=data)
model
summary(model)
```
Soooo p-values are different but everything this is supposed to be significant is. This is an analysis that produces output similar to what she presents in the paper. In the paper, she also talks about how 15 observations were automatically eliminated by the software, but nothing is being automatically eliminated in my analysis, so this might also be contributing to the different p-values. 
```{r}
survdiff(Surv(day, attacks) ~ species, data=data)
pairwise_survdiff(Surv(day, attacks) ~ species, p.adjust.method = "BH",
     data = data)
```

```{r}
coxph(Surv(day, attacks) ~ species, data=data)

```



```{r}
install.packages('RVAideMemoire')
library(RVAideMemoire)
library(survival)
library(survminer)
library(multcomp)
###soo R isn't recognizing the surv.multcomp function and I don't know why
surv.multicomp(Surv(day, attacks) ~ species,data = data, strata = NULL, type = "coxph", p.method = "fdr")
```


```{r}
plot(model, xlab="Time (days)", 
           ylab="Survivorship",
           ylim = c(0.85, 1.0), 
           xlim = c(1, 5))
```

```{r}
library(tayloRswift)
library(ggpubr)

compare_means(day ~ species,  data = data, method = "anova")

p <- ggsurvplot(fit = model, 
           palette = c("taylorRed"),
           xaxt = "n",
           xlab="Time (days)", 
           ylab="Survivorship",
           ylim = c(0.85, 1.0), 
           xlim = c(1, 5),  
           data = data, 
           axes = FALSE, 
           label = "map.signif")

p

##rename the x axis values 
p$plot <- p$plot + 
                  scale_x_continuous(breaks = c(1,2,3,4,5),
                                     labels = c(0,1,2,3,4))


p$plot
```
```{r}
compare_means(ipiclus ~ everete,  data = data, method = "anova")

# Visualize: Specify the comparisons you want
my_comparisons <- list( c("0.5", "1"), c("1", "2"), c("0.5", "2") )
ggboxplot(ToothGrowth, x = "dose", y = "len",
          color = "dose", palette = "jco")+ 
  stat_compare_means(comparisons = my_comparisons)+ # Add pairwise comparisons p-value
  stat_compare_means(label.y = 50)     # Add global p-value
```


```{r}
library(tayloRswift)
p <- ggsurvplot(fit = model, 
           xaxt = "n",
           xlab="Time (days)", 
           ylab="Survivorship",
           ylim = c(0.85, 1.0), 
           xlim = c(1, 5),  
           data = data, 
           axes = FALSE, 
           linetype = 8)

##use Red (Taylor's Version) color palette 
p$plot <- p$plot + scale_color_taylor(palette = "lover")
p$plot <- p$plot + theme_minimal()
p$plot

##rename the x axis values 
p$plot <- p$plot + 
                  scale_x_continuous(breaks = c(1,2,3,4,5),
                                     labels = c(0,1,2,3,4))
p$plot


```

```{r}
library(tayloRswift)
```
